### 2016-09-28 FrontBackmatter/Colophon.tex
Contributions written
Fix some missing references in CC chapter
Adjust colophon

\pdfbookmark[0]{Colophon}{colophon}
\section*{Colophon}
This document was typeset using the typographical look-and-feel
\texttt{classicthesis} developed by Andr\'e Miede. The style was
inspired by Robert Bringhurst's seminal book on typography ``\emph{The
Elements of Typographic Style}''. \texttt{classicthesis} is available
for both \LaTeX\ and \mLyX:
\begin{center}
\url{https://bitbucket.org/amiede/classicthesis/}
\end{center}

\bigskip

\noindent\finalVersionString

\emph{Garamond} and \emph{XITS} type faces are used.

>>>>

\pdfbookmark[0]{Colophon}{colophon}
\section*{Colophon}
This document was typeset using \XeLaTeX, with the
\texttt{classicthesis} template developed by André Miede.\footnote{\url{https://bitbucket.org/amiede/classicthesis/}}
The style was inspired by Robert Bringhurst's seminal book on typography
\emph{The Elements of Typographic Style}.\autocite{Bringhurst2004-wn}
The bibliography was processed using
Biblatex\footnote{\url{https://www.ctan.org/pkg/biblatex}} and
Biber.\footnote{\url{http://biblatex-biber.sourceforge.net/}}
David J. Perry's Cardo provides both the text and display typeface.
Open Sans is the sans-serif typeface, while Bitstream Vera Mono is used
for monospaced text.
Finally, XITS acts at the math typeface.

\bigskip
{\small
\noindent\myTitle
\\
\noindent\textcopyright\,\finalVersion, \myName
}
